Self-Supervised Learning of Generalized Policies in adversarial domains

### 2021-05-31 doc/paper/paper.tex
doc update

@@

\subsubsection{Example of Game}
\begin{Verbatim}[fontsize=\footnotesize]
.  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
t  t  #  t  t  #  t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #  .  .  #  .  .  #
t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #
t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #
\end{Verbatim}

@@

\subsubsection{Example of Game}
\begin{Verbatim}[fontsize=\footnotesize]
p.... # p.... # p.... # p.... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... #
..... # ..... # ..... # .A... # .A... # pA... # .A... # ..... # ..... # ..... # ..... # ..... # ..... #
..... # ..... # A.... # ..... # ..... # ..... # ..... # ..A.. # .pA.. # ..A.. # ..... # ..... # ..... #
..... # .A... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ...A. # ..... # ..... #
A...D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....A # ....A #
\end{Verbatim}

>>>>

The sections broken down into each domain are: Description of the domain, the training instances used to discover the policy, the learned features, description of the features, learned policy, description of the policy, and finally an example of a possible game, from initial state to goal, using the discovered policy in a test instance against an expert adversary. The initial state of the example test instance is taken from the infinite set of possible instances in the domain.

@@

\subsubsection{Example of Game}
\begin{Verbatim}[fontsize=\footnotesize]
.  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
.  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
.  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
t  t  #  t  t  #  t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #  .  .  #  .  .  #
t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #
t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #
t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #
t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #
\end{Verbatim}

@@

\subsubsection{Example of Game}
\begin{Verbatim}[fontsize=\footnotesize]
p.... # p.... # .p... # .p... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... #
..... # ..... # ..... # .A... # .A... # pA... # .A... # ..... # ..... # ..... # ..... # ..... # ..... #
..... # ..... # A.... # ..... # ..... # ..... # ..... # ..A.. # .pA.. # ..A.. # ..... # ..... # ..... #
..... # .A... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ...A. # ..... # ..... #
A...D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....A # ....A #
\end{Verbatim}
